Re-finding to support a Deep Web Question Answering System

### 2010-03-04 trunk/paper/semsearch10/content/ssq_ranking.tex

\subsection{SSQ Ranking}
In order to match a new query with a SSQ within our data store, we have defined similarity measures between the ontologies of the new query and the candidate SSQs. These measures capture the distance between the ontology classes, properties, and individuals at the conceptual level in addition to simply matching URIs. The similarity measures are implemented in two scenarios: \textit{on-line execution} and \textit{off-line mode}. The \textit{on-line execution} is time sensitive and is used primarily for relating newly defined SSQs to the SSQs in the store. During \textit{off-line execution}, the system clusters similar SSQs.

The similarity measure for the SSQ ontologies is determined by the following components.
\begin{enumerate}
    \item QueryClass: an OWL class and the root of the SSQ ontology structure.
    \item hasRealm: an OWL object property with its domain as the SSQ Query class and its range as a realm class.
    \item Contexts such as who, what, when, and where are OWL object properties, whose domains are the query classes and ranges are OWL classes. 
    \item SSQClass: an OWL class which is created from the components described above.
\end{enumerate}
Based on this ontology structure and the execution scenarios, we have created an algorithm for finding the matches between SSQ ontologies. It is based on class divergence, which is motivated by the concept of multiple dispatch in CLOS \cite{95411} and Dylan programming \cite{DBLP:conf/oopsla/BarrettCHMPW96} for generic function type matches. We consider the realm class and context property ranges for determining SSQ similarity. Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.

\subsubsection{Class Divergence}
\label{sec:ctd}
We employ a measure of compatibility, which we call \textit{class divergence}, between a source class and a target class using the \textit{topological structure} of the context classes in the ontology. We write $S \prec T$ for the reflexive transitive closure of the superclass relation. Let $d(P,Q)$ represent the hop distance in the directed ontology inheritance graph from $P$ to $Q$. The divergence between a source and target class ranges from zero (for identical classes) to one (for incompatible classes).  Let $S$ be the source class, $T$ be the target class, and let $C$ be a common ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$. The class divergence between $S$ and $T$, the unnormalized class dissimilarity, is defined as follows:

@@

%-------------------------------------------------------------------------------
\subsubsection{SSQ Ontology Matching}
\label{sec:oqom}

>>>>

\section{SSQ Ranking}
\label{sec:ssq}
In order to match a new query with a SSQ within our data store, we
have defined similarity measures between the ontologies of the new
query and the candidate SSQs. These measures capture the distance
between the ontology classes, properties, and individuals at the
conceptual level in addition to simply matching URIs. The similarity
measures are implemented in two scenarios: \textit{on-line execution}
and \textit{off-line mode}. The \textit{on-line execution} is time
sensitive and is used primarily for relating newly defined SSQs to the
SSQs in the store. During \textit{off-line execution}, the system
clusters similar SSQs.

The similarity measure for the SSQ ontologies is determined by the
following components.
\begin{enumerate}
    \item QueryClass: an OWL class and the root of the SSQ ontology
      structure.
    \item hasRealm: an OWL object property with its domain as the SSQ
      Query class and its range as a realm class.
    \item Contexts such as who, what, when, and where are OWL object
      properties, whose domains are the query classes and ranges are
      OWL classes.
    \item SSQClass: an OWL class which is created from the components
      described above.
\end{enumerate}
Based on this ontology structure and the execution scenarios, we have
created an algorithm for finding the matches between SSQ
ontologies. It is based on class divergence, which is motivated by the
concept of multiple dispatch in CLOS \cite{95411} and Dylan
programming \cite{DBLP:conf/oopsla/BarrettCHMPW96} for generic
function type matches. We consider the realm class and context
property ranges for determining SSQ similarity. Once we have the similarity measures between the user defined SSQ and relevant QRMs in the store, we can order the relevant QRMs. The order provides a ranking for the results to the user. Subsections \ref{sec:ctd}, and \ref{sec:oqom} describe about this in detail.

\subsection{Class Divergence}
\label{sec:ctd}
We employ a measure of compatibility, which we call \textit{class
  divergence}, between a source class and a target class using the
\textit{topological structure} of the context classes in the
ontology. We write $S \prec T$ for the reflexive transitive closure of
the superclass relation. Let $d(P,Q)$ represent the hop distance in
the directed ontology inheritance graph from $P$ to $Q$. The
divergence between a source and target class ranges from zero (for
identical classes) to one (for incompatible classes).  Let $S$ be the
source class, $T$ be the target class, and let $C$ be a common
ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$. The class
divergence between $S$ and $T$, the unnormalized class dissimilarity,
is defined as follows:

@@

%-------------------------------------------------------------------------------
\subsection{SSQ Ontology Matching}
\label{sec:oqom}
